\years{2019} \emph{Solution Formulas for Differential Sylvester and
Lyapunov Equations}. Calcolo, accepted for publication. (with M. Behr and P. Benner -- my share: 30\%) \\

\years{2018} \emph{{Space-Time Galerkin POD with application in optimal control of semi-linear parabolic partial differential equations}}. SIAM Journal on Scientific Computing, Vol. 40(3), pp. A1611--A1641. (with P. Benner and M. Baumann -- my share: 80\%) \\

\years{2018} \emph{Regularization and Rothe Discretization of Semi-Explicit Operator DAEs}. International Journal of Numerical Analysis and Modeling, Vol. 15(3), pp. 452--477. (with R. Altmann -- my share: 30\%) \\

\years{2018} \emph{Exponential Stability and Stabilization of Extended Linearizations via Continuous Updates of Riccati Based Feedback}. International Journal of Robust and Nonlinear Control, Vol. 28, pp. 1218--1232. (with P. Benner -- my share: 90\%) \\

\years{2018} \emph{Optimal Control of a Stefan Problem Fully Coupled with Incompressible Navier-Stokes-Equations and Mesh Movement}. Analele Stiintifice ale Universitatii Ovidius Constanta - Seria Matematica, 26(2), 11--40. (with B. Baran, P. Benner, J. Saak -- my share 20\%) \\

\years{2017} \emph{Moment-Matching Based Model Reduction for Navier--Stokes Type Quadratic-Bilinear Descriptor Systems}. ZAMM - Journal of Applied Mathematics and Mechanics, online first. (with M. I. Ahmad, P. Benner, and P. Goyal -- my share: 40\%) \\

\years{2017} \emph{Simulation of Multibody Systems with Servo Constraints through Optimal Control}. Multibody System Dynamics, Vol. 40(1), pp. 75--98. (with R. Altmann -- my share: 50\%) \\

\years{2016} \emph{A Differential-Algebraic Riccati Equation for Applications in Flow Control}. SIAM Journal on Control and Optimization, Vol. 54(2), pp. 718--739.}\\

\newpage

\years{2015} \emph{Finite Element Decomposition and Minimal Extension for Flow Equations}. M2AN - Mathematical Modelling and Numerical Analysis, Vol. 49(5), pp. 1489--1509. (with R. Altmann -- my share: 50\%) \\

\years{2015} \emph{Time-dependent Dirichlet Conditions in Finite Element Discretizations}. ScienceOpen Research. (with P. Benner -- my share: 90\%)\\

\years{2012} \emph{Distributed Control of Linearized Navier--Stokes Equations via Discretized Input/Output Maps}. ZAMM - Journal of Applied Mathematics and Mechanics. Vol. 92(4), pp. 257--274. (with V. Mehrmann -- my share: 80\%) 


