\years{2018} \emph{Continuous, Semi-discrete, and Fully Discretised Navier-Stokes Equations}. In DAE Forum Volume \emph{Applications of Differential-Algebraic Equations: Examples and Benchmarks}, to appear. (with R. Altmann -- my share: 60\%) \\

\years{2017} \emph{Nonlinear Stabilizing Feedback Design for Incompressible Flows via Updated Riccati-Based Gains}. Proceedings of the Proceedings of the IEEE Conference on Decision and Control 2017, accepted. (with P. Benner -- my share: 90\%) \\ 

\years{2017} \emph{Convergence of Approximations to Riccati-based Boundary-feedback Stabilization of Laminar Flows}. IFAC-PapersOnLine IFAC, Vol. 50(1), pp. 12296-12300. (with P. Benner -- my share: 90\%)\\

\years{2016} \emph{Robust Stabilization of Laminar Flows in Varying Flow Regimes}. IFAC-PapersOnLine, IFAC. Vol. 49(8), pp. 31-36. (with P. Benner -- my share: 90\%)\\

\years{2015} \emph{Discrete Input/Output Maps and their Relation to Proper Orthogonal Decomposition}. Numerical Algebra, Matrix Theory, Differential-Algebraic Equations and Control Theory. Festschrift in Honor of Volker Mehrmann. Springer, pp. 585-608. (with M. Baumann and M. Schmidt -- my share: 60\%) \\

\years{2015} \emph{LQG-Balanced Truncation Low-Order Controller for Stabilization of Laminar Flows}. Active Flow and Combustion Control 2014, Springer. pp. 365-379. (with P. Benner -- my share: 90\%) \\

\years{2010} \emph{A new discretization framework for input/output maps and its application to flow control}. Active Flow Control. Papers contributed to the Conference, Springer, pp. 357-372. (with V. Mehrmann and M. Schmidt -- my share: 60\%) 


