%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compact Academic CV
% LaTeX Template
% Version 1.0 (10/6/2012)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Dario Taraborelli (http://nitens.org/taraborelli/home)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important:
% This template needs to be compiled using XeLaTeX
%
% Note: this template has the option to use the Hoefler Text font, see the
% font configurations section below for instructions on using this font
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{article} % Document font size and paper size

\usepackage{fontspec} % Allows the use of OpenType fonts

\usepackage{geometry} % Allows the configuration of document margins
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in} % Document margin settings
\setlength\parindent{0in} % Remove paragraph indentation

\usepackage[usenames,dvipsnames]{xcolor} % Custom colors

\usepackage{sectsty} % Allows changing the font options for sections in a document
\usepackage[normalem]{ulem} % Custom underlining
\usepackage{xunicode} % Allows generation of unicode characters from accented glyphs
\defaultfontfeatures{Mapping=tex-text} % Converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

\usepackage{marginnote} % For margin years
\newcommand{\years}[1]{\marginnote{\scriptsize #1}} % New command for including margin years
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt} % Slightly increase the distance of the margin years from the contant
\reversemarginpar

\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={Jan Heiland - vita},pdfauthor={Jan Heiland}]{hyperref} % PDF setup - set your name and the title of the document to be incorporated into the final PDF file meta-information
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} % Link colors

%----------------------------------------------------------------------------------------
%	FONT CONFIGURATIONS
%----------------------------------------------------------------------------------------

% Two font choices are available in this template, the default is Linux Libertine, available for free at: http://www.linuxlibertine.org while the secondary choice is Hoefler Text which comes bundled with Mac OSX.
% To use Hoefler Text, comment out the Linux Libertine block below and uncomment the Hoefler Text block. You will also need to replace the "\&" characters with "\amper{}" in section titles.

% Linux Libertine Font (default)
\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O} % Main text font
%\setmonofont[Scale=0.8]{Monaco} % Set mono font (e.g. phone numbers)
\sectionfont{\sffamily\mdseries\upshape\Large} % Set font options for sections
\subsectionfont{\sffamily\mdseries\upshape\normalsize} % Set font options for subsections
\subsubsectionfont{\sffamily\mdseries\upshape\large} % Set font options for subsubsections
% \chardef\&="E050 % Custom ampersand character

%----------------------------------------------------------------------------------------

\begin{document}
\sffamily
%----------------------------------------------------------------------------------------
%	CONTACT AND GENERAL INFORMATION SECTION
%----------------------------------------------------------------------------------------

{\LARGE Jan Heiland}\\[1cm] % Your name
Max-Planck-Institut f\"ur Dynamik komplexer technischer Systeme\\ % Your address
Sandtorstr. 1\\
39106 Magdeburg \\[.2cm]
Phone: \texttt{0391-6110-476}\\ [.2cm]
Email: \href{mailto:heiland@mpi-magdeburg.mpg.de}{heiland@mpi-magdeburg.mpg.de}\\ % Your email address
Home: \href{http://www.mpi-magdeburg.mpg.de/823023/cacsd}{www.mpi-magdeburg.mpg.de/823023/cacsd}\\ % Your academic/personal website
Home: \href{http://www.janheiland.de}{www.janheiland.de}\\[.3in] % Your academic/personal website

% \vfill % Whitespace between contact information and specific CV information

%------------------------------------------------

Born: January 21, 1983---Friedrichshafen, Germany\\ % Your date of birth
Nationality: German

%------------------------------------------------

\section*{Current Position}

\emph{Team Leader} at the Max Planck Institute for Dynamics of Complex Technical Systems \\ \emph{Junior Professor} at the Otto-von-Guericke University Magdeburg% Your current or previous employment position

%------------------------------------------------

\section*{Areas of Specialization}

\textbf{Differential-algebraic Equations}, \textbf{Navier-Stokes Equations}, \textbf{Optimal Control},  \\System Theory, Model Reduction, Numerical Analysis

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section*{Academic Career}

\years{2007--2009}Student Employee at Bombardier Transportation, Department \emph{Special Engineering for Aerodynamics and Acoustics}, Berlin\\
\years{2009--2013}Full-time research assistant at TU Berlin, Department of Mathematics, Berlin\\
\years{since 2013}Postdoc at MPI Magdeburg, Department \emph{Computational Methods in Systems and Control Theory}, Magdeburg\\
\years{since 2014}Team leader of the team \emph{Computer Aided Control System Design} at the MPI Magdeburg\\
\years{since 2018}Jun.Prof. for \emph{Numerical Methods for Descriptor Systems} at the OVGU Magdeburg\\

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section*{Education}

\years{2009}\textsc{Diploma} in technical mathematics, TU Berlin\\
\years{2014}\textsc{PhD} in mathematics, TU Berlin

%----------------------------------------------------------------------------------------
%	GRANTS, HONORS AND AWARDS SECTION
%----------------------------------------------------------------------------------------

\newpage
\section*{Scholarships, Research Stays \& Honours}
\years{2010--2013}PhD scholarship by \emph{Studienstiftung des dt. Volkes}\\
\years{2012}Research stay at TUCOROM Poitiers, France, invited by Prof. B. Noack\\
\years{2014}\emph{Research in Pairs} at \emph{Mathematisches Forschungsinstitut Oberwolfach}\\
\years{2015\&2016} Research stay at Shanghai University, China, as part of the \emph{Recruitment Program of High-end Foreign Experts}\\
\years{2017} \emph{DAAD travel award} for visiting the \emph{56th IEEE Conference on Decision and Control} in Melbourne, Australia\\
\years{since 2015} Open Access Ambassador of the \emph{Max Planck Society}

\section*{Service to the Community}
\years{since 2014} Reviewer for  \emph{Acta Appl. Math.} --- \emph{Automatica} --- \emph{Electron. Trans. Numer. Anal.} --- \emph{Math. Control Signals Systems} --- \emph{SIAM J. Sci. Comput.} --- and several conference proceedings\\
\years{2015}Organization of a young researcher minisymposium on \emph{Analysis, Applications and Approximation of Constrained PDEs} at the GAMM annual meeting in Lecce, Italy\\
\years{2015}Organization of a minisymposium on \emph{Numerical Approximation of DAEs and Constrained PDEs with Applications} at the ICIAM 2015 in Beijing, China\\
\years{2016}Organization of the workshop \emph{Modelling, Model Reduction, and Optimization of Flows} in Shanghai, China \\
\years{2017}Organization of the minisymposium \emph{MS 28 -- Model reduction methods for simulation and (optimal) control} at the Enumath 2017 in Voss, Norway\\
\years{2018}Organization of a young researcher workshop \emph{Analysis and Numerical Approximation of Constrained Systems} in Sion, Switzerland\\
\years{2018}Chair of the focus session \emph{Model order reduction and low-rank approximation for nonlinear problems } at the EUCCO2018 in Trier, Germany
\newpage
\section*{Teaching}
\subsection*{Courses}
\years{2015} Short Course on \emph{Model Reduction of Linear Time Invariant Systems}. Shanghai University, Shanghai, China\\
\years{2016} Course (4 SWS) on \emph{Differential Algebraic Equations}. Summer Term 2016. Otto-von-Guericke-Universität, Magdeburg \\
\years{2017} Course (4 SWS) on \emph{Funktionentheorie Lehramt}. Winter Term 2017. Otto-von-Guericke-Universität, Magdeburg \\
\years{2018} Short Course on \emph{Tensor Techniques} for the \emph{Graduiertenkolleg}. Otto-von-Guericke-Universität, Magdeburg
\subsection*{Tutorials}
\years{2010--2012} \emph{Mathematik für PhysikerInnen IV}, \emph{Numerik 1 f\"ur Ingenieure} and \emph{Numerik 2}. TU Berlin
\subsection*{BA/MA Theses}
\years{2011} Manuel Baumann, BA, TU Berlin: \emph{Modellierung und Simulation von Dispersionen in turbulenter Strömung}\\
\years{2015} Max Behr, MA, Otto-von-Guericke-Universität Magdeburg: \emph{Optimierung und Stabilisierung von inkompressiblen Strömungen in M.E.S.S.}\\
\years{2016} Bj\"orn Baran, MA, Otto-von-Guericke-Universität Magdeburg: \emph{Optimal Control of a Stefan Problem with Gradient-Based Methods in FEniCS}

\subsection*{Supervision of PhD Projects}
\years{since 2016} Max Behr, Otto-von-Guericke-Universität Magdeburg: \emph{Modellreduktion und Optimalsteuerung von linearen zeitveränderlichen und parameterabhängigen Systemen}\\
\years{since 2016} Bj\"orn Baran, Otto-von-Guericke-Universität Magdeburg: \emph{Riccati Based Feedback Control of Complex Flows}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS AND TALKS SECTION
%----------------------------------------------------------------------------------------
\newpage
\section*{Third party funding}

\years{2017} DAAD -- travel grant -- 2700 Euro \\

\years{2016} \emph{Chinesisch-Deutsches Zentrum f\"ur Wissenschaftsf\"orderung} -- financing of an international workshop\footnote{For political reasons, Prof. Peter Benner appeared as the author of the proposal. Prof. Peter Benner \href{mailto:benner@mpi-mageburg.mpg.de}{benner@mpi-magdeburg.mpg.de} will be happy to confirm that the successful proposal was set up and written mainly by me.} -- 275500 RMB (about 36700 Euro) for local expenses plus 25500 Euro for international travel \\

\years{2015\&2016} \emph{Chinese State Admistration of Foreign Experts Affairs} and \emph{International Office of Shanghai University} -- funding for travel and research stays -- 50000 RMB (about 6700 Euro) \& 61000 RMB (about 8100 Euro)


\newpage
\section*{Publications}

\vspace{.1in}
\subsection*{Journal Publications}

\years{2018} \emph{Space-Time Galerkin POD with application in optimal control of semi-linear parabolic partial differential equations}. SIAM Journal on Scientific Computing, to appear. (with P. Benner and M. Baumann) \\

\years{2018} \emph{Regularization and Rothe Discretization of Semi-Explicit Operator DAEs}. International Journal of Numerical Analysis and Modeling, Vol. 15(3). pp. 452-477. (with R. Altmann) \\

\years{2017} \emph{Exponential Stability and Stabilization of Extended Linearizations via Continuous Updates of Riccati Based Feedback}. International Journal of Robust and Nonlinear Control, online first. (with P. Benner) \\

\years{2017} \emph{Moment-Matching Based Model Reduction for Navier--Stokes Type Quadratic-Bilinear Descriptor Systems}. ZAMM - Journal of Applied Mathematics and Mechanics, online first. (with M. I. Ahmad, P. Benner, and P. Goyal) \\

\years{2017} \emph{Simulation of Multibody Systems with Servo Constraints through Optimal Control}. Multibody System Dynamics, Vol. 40(1), pp. 75-98. (with R. Altmann) \\

\years{2016} \emph{A Differential-Algebraic Riccati Equation for Applications in Flow Control}. SIAM Journal on Control and Optimization, Vol. 54(2), pp. 718-739.\\

\years{2015} \emph{Finite Element Decomposition and Minimal Extension for Flow Equations}. M2AN - Mathematical Modelling and Numerical Analysis, Vol. 49(5), pp. 1489-1509. (with R. Altmann) \\

\years{2015} \emph{Time-dependent Dirichlet Conditions in Finite Element Discretizations}. ScienceOpen Research. (with P. Benner)\\

\years{2012} \emph{Distributed Control of Linearized Navier--Stokes Equations via Discretized Input/Output Maps}. ZAMM - Journal of Applied Mathematics and Mechanics. Vol. 92(4), pp. 257-274. (with V. Mehrmann) 


\vspace{.1in}
\newpage
\subsection*{Peer-reviewed Conference Proceedings and Book Chapters}

\years{2018} \emph{Continuous, Semi-discrete, and Fully Discretised Navier-Stokes Equations}. In DAE Forum Volume \emph{Applications of Differential-Algebraic Equations: Examples and Benchmarks}, to appear. (with R. Altmann) \\

\years{2017} \emph{Nonlinear Stabilizing Feedback Design for Incompressible Flows via Updated Riccati-Based Gains}. Proceedings of the Proceedings of the IEEE Conference on Decision and Control 2017, accepted. (with P. Benner) \\ 

\years{2017} \emph{Convergence of Approximations to Riccati-based Boundary-feedback Stabilization of Laminar Flows}. IFAC-PapersOnLine IFAC, Vol. 50(1), pp. 12296-12300. (with P. Benner)\\

\years{2016} \emph{Robust Stabilization of Laminar Flows in Varying Flow Regimes}. IFAC-PapersOnLine, IFAC. Vol. 49(8), pp. 31-36. (with P. Benner)\\

\years{2015} \emph{Discrete Input/Output Maps and their Relation to Proper Orthogonal Decomposition}. Numerical Algebra, Matrix Theory, Differential-Algebraic Equations and Control Theory. Festschrift in Honor of Volker Mehrmann. Springer, pp. 585-608. (with M. Baumann and M. Schmidt) \\

\years{2015} \emph{LQG-Balanced Truncation Low-Order Controller for Stabilization of Laminar Flows}. Active Flow and Combustion Control 2014, Springer. pp. 365-379. (with P. Benner) \\

\years{2010} \emph{A new discretization framework for input/output maps and its application to flow control}. Active Flow Control. Papers contributed to the Conference, Springer, pp. 357-372. (with V. Mehrmann and M. Schmidt) 

\vspace{.1in}
\subsection*{Proceedings and Posters}
\years{2015} \emph{A generalized POD space-time Galerkin scheme for parameter dependent dynamical systems}. Poster at MoRePaS 2015 - Model Reduction of Parametrized Systems III, Trieste, Italy. (with M. Baumann and P. Benner)\\

\years{2010} \emph{Simulation and Control of Drop Size Distributions in Stirred Liquid/Liquid Systems}. Proc. 4th International Conference on Population Balance Modelling, September 15-17 2010, Berlin. (with M. Baumann, A. Walle, V. Mehrmann, and M. Schäfer)\\

\years{2009} \emph{Shape Optimization in Train Aerodynamics}. Proceedings of Euromech Colloquium 509 Vehicle Dynamics, Berlin. (with A. Herbst, J. Mauss, and A. Orellano)


\newpage
\subsection*{Selected Preprints}


\years{2017} \emph{Example Setups of Navier--Stokes Equations with Control and Observation: Spatial Discretization and Representation via Linear-quadratic Matrix Coefficients}. arXiv:1707.08711. (with M. Behr and P. Benner) \\

\years{2016} \emph{Best Practices for Replicability, Reproducibility and Reusability of Computer-Based Experiments Exemplified by Model Reduction Software}. arXiv:1607.01191. (with J. Fehr, C. Himpe, and J. Saak)\\


\years{2016} \emph{Space-time Galerkin POD with application in optimal control of semi-linear parabolic partial differential equations}. arXiv:1611.04050. (with M. Baumann and P. Benner) \\

\years{2015} \emph{Simulation of Multibody Systems with Servo Constraints through Optimal Control}. Oberwolfach Preprint OWP 2015-18. (with R. Altmann)

\newpage
\vspace{.1in}
\subsection*{Theses}
\years{2014} PhD thesis -- \emph{Decoupling and optimization of differential-algebraic equations with application in flow control}. TU Berlin.\\

\years{2009} Diploma thesis -- \emph{Distributed Control of Semidiscretized Oseen Equations}. TU Berlin.

\vspace{.1in}
\subsection*{Publication of Code}

\years{2017}\texttt{nse-quadform-mats}. Data and example code for pure \emph{Python/Octave/Matlab} implementations of example setups of distributed or boundary control of incompressible flows. \href{https://doi.org/10.5281/zenodo.834940}{DOI:10.5281/zenodo.834940} \\

\years{2017}\texttt{spacetime-genpod-burgers}. A \emph{Python} implementation of a generalized space-time POD method with application to optimal control of the Burgers' equation. \\ \href{http://doi.org/10.5281/zenodo.583296}{DOI:10.5281/zenodo.583296}\\

\years{2016}\texttt{NSE-DAE-Riccati}. A \emph{Python} implementation of an index-2 differential Riccati equation solver for the solution of tracking problems for Navier-Stokes equations. \\ \href{http://doi.org/10.5281/zenodo.192348}{DOI:10.5281/zenodo.192348}\\

\years{2014}\texttt{lqgbt-oseen}. A \emph{Python} implementation of the LQGBT approach to low-dimensional controllers for the stabilization of incompressible flows. Application example: Stabilization of the cylinder wake.\\

\years{2014}\texttt{dolfin-navier-scipy}. A \emph{Python} interface between \emph{FEniCS} for Finite Element discretizations of flow equations and \emph{Scipy} for time integration, model reduction, or control algorithms.
\vfill
For weblinks to the publications see \href{http://www.janheiland.de/publications}{www.janheiland.de/publications}
%------------------------------------------------

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

% \vfill{} % Whitespace before final footer
% 
% %----------------------------------------------------------------------------------------
% %	FINAL FOOTER
% %----------------------------------------------------------------------------------------
% 
% \begin{center}
% {\scriptsize Last updated: \today\- •\- \href{http://www.LaTeXTemplates.com}{http://www.LaTeXTemplates.com}} % Any final footer text such as a URL to the latest version of your CV, last updated date, compiled in XeTeX, etc
% \end{center}
% 
% %----------------------------------------------------------------------------------------

\end{document}
